### 2018-08-28 manuscript.tex
Update manuscript.tex

\subsection{Research Questions}\label{research-questions}
There are two main research questions in this study:  attitudes of FGC benefits (see the list of FGC benefits at table xx) in association with attitudes of FGC continuance; and attitudes of FGC benefits and of FGC continuance in association with intention (planned behavior) of cutting daughters.  The first question is referred to a FGC future model (FGC attitude model?), and the second a FGC daughter model (FGC intention model?).

\_\_{[}CF: how about the third model xx basic daughter model without counting attitudes of FGC continuance ?  A few sentence of the differences between FGC future model and FGC daughter model{]}

@@

The were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires for this study.  We first chose nations with high FGC prevalence \cite{UNIC16}, then their DHS surveys with modules of FGC benefits, and index of gender awareness.  The following countries met the criteria:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We did not use a newer dataset from those countries due to the lack of FGC benefits information in the newer surveys (checked in 09/17).

>>>>

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze attitudes of FGC benefits (see the list of FGC benefits at table xx) and of FGC continuance in association with intention (planned behavior) to cut daughters.  Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits and intention (planned behavior) of cutting daughters in the hope of???

@@

There were two primary sources of FGC data: the Demographic and Health Surveys (DHS) by USAID and and the Multiple Indicator Cluster Survey (MICS) directed by UNICEF \cite{CappMone13, YodeWang13}. We used DHS data for this study because of certain questionnaires only available in DHS.  Countries with the following criteria were selected:  high FGC prevalence \cite{UNIC16}, DHS surveys with modules of FGC benefits, and index of gender awareness; and that resulted in four nations:  Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  We were not able to use newer dataset from those countries due to the lack of FGC benefits modules (checked in 09/17).
